I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-11 Paper/Paper_noProof.tex
fig1

\begin{figure}[t!]
	\centering
		\includegraphics[scale=0.4]{example.png}
	\caption{A DNN example from \cite{kneuron}, where every node is separated into its linear and its ReLU functions.}
	\label{fig1}
	\end{figure}

>>>>

%\begin{figure}[t!]
%	\centering
%		\includegraphics[scale=0.4]{example.png}
%	\caption{A DNN example from \cite{kneuron}, where every node is separated into its linear and its ReLU functions.}
%	\label{fig1}
%	\end{figure}

			\node[circle, draw= purple, thick, minimum width = 20,
			minimum height = 20] (input1) {$x_1$};

			\node[circle, draw= purple, thick, minimum width = 20,
			minimum height = 20] (input2) at ($(input1) + (0,-1.5)$) {$x_2$};

			% Hidden layers
			\node[circle, draw= black, thick, minimum width = 20,
			minimum height = 20] (hidden1) at ($(input1) + (2.5,0)$) {$x_3$};
			\node[circle, draw= black, thick] (hidden2) at ($(input1) + (2.5,-1.5)$) {$x_4$};

			\node[circle, draw= black, thick, minimum width = 20,
			minimum height = 20] (hidden3) at ($(input1) + (5,0)$){$x_5$};
			\node[circle, draw= black, thick] (hidden4) at ($(input1) + (5,-1.5)$) {$x_6$};

			\node[circle, draw= blue, thick, minimum width = 20,
			minimum height = 20] (hidden5) at ($(input1) + (7.5,0)$){$x_7$};
			\node[circle, draw= blue, thick] (hidden6) at ($(input1) + (7.5,-1.5)$) {$x_8$};

			% Output layer
			\node[circle, draw= black, thick, minimum width = 20,
			minimum height = 20] (output1) at ($(input1) + (10,0)$){$x_9$};

			\node[circle, draw= black, thick, minimum width = 20,
			minimum height = 20] (output2) at ($(input1) + (10,-1.5)$){$x_{10}$};

			% Connections

			\draw[->,thick] ($(input1) + (-1.5,0)$) -- (input1) node[midway, above] {$[-1,1]$};

			\draw[->,thick] ($(input1) + (-1.5,-1.5)$) -- (input2) node[midway, above] {$[-1,1]$};

			\draw[->,thick] (input1) -- (hidden1) node[near start, above] {$1$};
			\draw[->,thick] (input1) -- (hidden2)node[near start, above] {$1$};

			\draw[->,thick] (input2) -- (hidden1) node[near start, above] {$1$};
			\draw[->,thick] (input2) -- (hidden2)node[near start, below] {$-1$};

			\draw[->,thick] (hidden1) -- (hidden3) node[midway, above] {$\max(x_1,0)$};
			\draw[->,thick] (hidden2) -- (hidden4) node[midway, above] {$\max(x_2,0)$};

			\draw[->,thick] (hidden3) -- (hidden5) node[near start, above] {$1$};			
			\draw[->,thick] (hidden3) -- (hidden6) node[near start, above] {$0$};

			\draw[->,thick] (hidden4) -- (hidden5)node[near start, above] {$2$};
			\draw[->,thick] (hidden4) -- (hidden6)node[near start, below] {$1$};

			\draw[->,thick] (hidden5) -- (output1) node[midway, above] {$\max(x_7,0)$};
			\draw[->,thick] (hidden6) -- (output2) node[midway, above] {$\max(x_8,0)$};

		\end{tikzpicture}
		\caption{A DNN example from \cite{kneuron}, where every node is separated into its linear and its ReLU functions.}
		\label{fig1}
	\end{figure}
